---
title: "FIT3152 Assignment 1"
author: "Ashley Yow Shu Ping 32227523"
output:
  pdf_document: default
  html_document: default
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

**Defining libraries**
``` {r libraries, result="hide"}
library(ggplot2)
library(tidyr)
library(dplyr)
library(reshape2) #the use of melt()
library(cluster) #for k-means clustering
library(factoextra) #for cluster plot
```

##### **Question 1**

**Reading the data from the CSV file**

```{r readfile}
rm(list = ls())
set.seed(32227523)  
cvbase = read.csv("PsyCoronaBaselineExtract.csv")
cvbase <- cvbase[sample(nrow(cvbase), 40000), ]
```

**Descriptive analysis on the data**

Dimension of the data: There are 40000 rows and 54 columns in this data set. A
summary of the data set is also generated to have a general overview of each
attribute.
```{r dimensions_summary, results="hide"}
dim(cvbase)
summary (cvbase)
```

As for the analysis of data types, the data set is of type list, and there
are two different data types within the list itself, where all attributes except
coded_country (is of type character) belong to the integer data type. From 
here we can clearly conclude that out of 54 attributes that exists in the data 
set, only 1 attribute (coded_country) is a non-numerical attribute, whilst the 
remaining 53 attributes appear to be numerical attributes.
```{r datatype, results='hide'}
typeof(cvbase)
str(cvbase)
```

The distribution of numerical attributes is represented as bar graphs in small
multiples. According to the bar charts, negative affects such as Anxious, Bored,
Depressed, Nervous and Exhausted are mostly positively skewed. AffDepr was the
most positively skewed, which means majority of people who participated in the 
survey are very slightly or not at all depressed during the early stages of the
pandemic. As for positive affects, Calm, Content and Relaxed are close to being
symmetrically skewed, which depicts many feeling rather neutral in these 
emotions. Affects like Energetic, Excited and Inspired are rather positively
skewed, very little people feeling energetic and inspired, and the majority felt
very slightly or not at all excited. The survey is responded by mostly adults
aged between 25 to 34, and those who are aged above 85 contribute the least
responses. Most participants of the survey received a Bachelors Degree as their
highest qualification. In terms of the Corona Community Injunctive Norms, all 
attributes are negatively skewed except for c19IsPunish, where c19NormShould is 
the most negatively skewed. It showed that the majority strongly agrees that 
people in their area should self-isolate and engage in social distancing. As for
c19IsPunish, it is closer to being symmetrically skewed, many believe that their 
community punishes those who deviate from the rules and puts them into place
at a moderate frequency (4 on a scale of 1 to 6, with 1 being not at all and 6 
represents very much). Oberserving the attributes for societal discontent, disc1
and disc2 are negatively skewed, and disc3 is rather symmetrically skewed. The
graphs show that people agree that things will go wrong in society and are
concerned for the future of society. People, too, disagree to the statement of 
being satisfied with society. Most people are employed and working 40 or more 
hours per week, while the least of the population are disabled and not able to
work. All Corona Pro-Social Behaviours graphs are negatively skewed, which shows
that a big part of the population are willing to be helpful and considerate
towards others to help ease the pandemic and the people who have been affected.
There are more male responders than female, and a small group of other genders.
fail01, happy, PLRAC19, PLRAEco, trustGovCtry, and trustGovState are attributes
that display a close to symmetrically skewed pattern. fail02, jbInsec01, jbInsec04
and PFS03 all show patterns of being positively skewed, whereas fail03, jbInsec02,
lifeSat, MLQ and PFS02 are all negatively skewed.

```{r distribution_of_attr}
#making a temp data frame that only has all numerical attributes
df = select(cvbase, -c(coded_country))
#plotting the attributes
df %>%
  pivot_longer(affAnx:c19ProSo04, names_to = "attribute", values_to = "response") %>%
  ggplot(aes(x = response)) +
  geom_bar(fill="coral", color="black") +
  facet_wrap(vars(attribute), ncol = 8) +
  labs(x = "Scale of Responses", y = "Frequency")
```

There is a total of 426718 missing values (NA) in this data set. Among the total
number of missing values, the attribute employstatus_8 has the most value of NA
which is 39265 records.
```{r missingvaluecount}
sum(is.na(cvbase))
#searching for the attribute with the most missing values
max_missingval = 0
max_index = 0
for(i in 1:ncol(cvbase)) {
  if (max_missingval < sum(is.na(cvbase[,i]))){
    max_missingval = sum(is.na(cvbase[,i]))
    max_index = i
  }
}
print(colnames(cvbase[max_index]))
print(max_missingval)
```

There are a total of 110 locations/countries (including unspecified locations) 
that participated in this survey from the sampled data set.
```{r countries_participated}
unique(cvbase$coded_country)
length(unique(cvbase$coded_country))
```

**Pre-processing the data file**

Rows with most NA are removed to simplify further analysis, the number 27 was 
chosen as there are a total of 54 attributes, and at least half of the
attributes are to have data in a record for it to give sufficient data. Records 
without a specified country is also removed. Since the employstatus attribute 
each have NA values close to the number of records (viewed from summary of cvbase), 
the columns will be dropped to prevent potential problems in modelling and prediction.
```{r removeNA_and_missingvalues}
clean_cvbase = cvbase[rowSums(is.na(cvbase)) < 27, ]
clean_cvbase = clean_cvbase[(clean_cvbase$coded_country != ""),]
clean_cvbase = select(clean_cvbase, -c(employstatus_1, employstatus_2, employstatus_3,
                                       employstatus_4, employstatus_5,employstatus_6,
                                       employstatus_7, employstatus_8, employstatus_9,
                                       employstatus_10))
```

Renumbering the row indexes
```{r index_renumbering}
rownames(clean_cvbase) <- 1:nrow(clean_cvbase)
```

##### **Question 2**

###### **2(a)**

**Focus country: Italy**

**Grouping the data by focus country and other countries**
```{r grouping}
focuscountry_data <- clean_cvbase[(clean_cvbase$coded_country == "Italy"),]
rownames(focuscountry_data) <- 1:nrow(focuscountry_data)
othercountries_data <- clean_cvbase[(clean_cvbase$coded_country != "Italy"),]
rownames(othercountries_data) <- 1:nrow(othercountries_data)
```

**Plotting out the distribution in attributes for both groups to observe differences**

Based on the chart depicting the responses of the two groups, in terms of how
affected people were, citizens of Italy expressed great discontent in comparison
to the rest of the world, with their response to that affect mostly being very 
slightly or not at all Content, whereas the majority of citizens from other 
countries felt moderately content. In Italy, more people appear to be very 
slightly or not at all calm than quite a bit calm, whereas people in other
countries are the contrary. In Italy, there are more people who feel uninspired 
at all than moderately inspired, whereas people in other countries are more
moderately inspired than totally uninspired.There appears to be some respondents 
aged between 65 to 75 in Italy, more in amount in relative comparison to other 
countries, but no one from the age group 85 and above responded the survey whereas 
in other countries, there appears to be a small group of elderly of that age. 
As for pro social behaviours, more citizens of Italy stand neutral when it comes
to their willingness to help others who suffer from the virus than to be somewhat
agreeing to this idea. In other countries, more people somewhat agree on helping
others who are suffering from the pandemic than not having an opinion about it
at all. The same pattern of observation can be made with c19ProSo02, with more 
people in Italy neither agree or disagree to be willing to make donations to those
who suffer from Coronavirus than to somewhat agree to it, and vice versa for
the people outside of Italy. As for the willingness to make personal sacrifices
to prevent the spread of the Coronavirus, the majority of Italians are strongly
willing to do so, in comparison to the majority in the other countries. The 
respondents of the survey in Italy have reached higher education as their highest
level of education, whereas the majority of others in the world have received a 
bachelors degree. In Italy, most people do not have an opinion on whether or not
their group is worst off in this pandemic compared to other people in the same 
country, whilst the majority in other countries have mostly disagreed with this
statement. Looking into job insecurities, most people in other countries feel 
pretty certain of their job security, and the majority in Italy stand neutral
in believing whether or not they might lose their job. In terms of the aspect of
perceived financial strain, the majority of people in Italy do not think they
are particularly strained nor not strained financially. Hence, they also stand
neutral on whether or not they find it difficult to pay for expenses. However, 
most people in other countries agree that they are financially strained, but
expressed otherwise when it comes to the ability to pay for expenses. 
```{r plotting}
#drop the column coded_country as it serves no purpose for graph plotting and comparisons
focuscountry_data = select(focuscountry_data, -c(coded_country))
othercountries_data = select(othercountries_data, -c(coded_country))

#plot small multiples of bar charts for focus country data
focuscountry_data %>%
  pivot_longer(affAnx:c19ProSo04, names_to = "attribute", values_to = "response") %>%
  ggplot(aes(x = response)) +
  geom_bar(fill="cyan", color="black") +
  facet_wrap(vars(attribute), ncol = 8) +
  labs(x = "Scale of Responses", y = "Frequency") +
  ggtitle("Italy Corona Baseline Survey Response")

#plot small multiples of bar charts for other countries data
othercountries_data %>%
  pivot_longer(affAnx:c19ProSo04, names_to = "attribute", values_to = "response") %>%
  ggplot(aes(x = response)) +
  geom_bar(fill="magenta", color="black") +
  facet_wrap(vars(attribute), ncol = 8) +
  labs(x = "Scale of Responses", y = "Frequency") +
  ggtitle("Other Countries Corona Baseline Survey Response")
```

###### **2(b)**

**Analysing how well participants responses in Italy predict c19ProSo01**

c19ProSo01 collects the information on how willing people are to help others who
suffer from Coronavirus. According to the summary of the fitted model using
linear regression, jbInsec02 and c19NormShould appears to be the best predictors 
for this pro social behaviour due to having the lowest p-values among the rest 
of the potential predictors. c19NormDo, c19IsOrg, gender and edu seem like 
potential predictors too (because a p-value lower than 0.05), but we would barely 
have enough evidence to prove of them being strong predictors. A correlation heat 
map is plotted to spot for attributes with potential relationships with each other.
The predictors above are shown to have greater relationship compared to the rest
as well. 

```{r focuscountry_pro1}
#create data sets with only the predictors and one pro-social attribute each for linear modelling
focuscountry_pro1 = select(focuscountry_data, -c(c19ProSo02, c19ProSo03, c19ProSo04))
#create a linear regression model for all pro-social attr
italy1.fit <-lm(c19ProSo01 ~ ., data = focuscountry_pro1, na.action = na.exclude)
#check for significant predictors for all pro-social attitude attributes
summary(italy1.fit)
#plotting a correlation heatmap for c19ProSo01
focus.cor1 = as.table(round(cor(focuscountry_pro1[1:40], 
                                    use = "pairwise.complete.obs"), digit = 2))
focus.cor1 = melt(focus.cor1) #convert table into long format
heatmap1 = ggplot(data = focus.cor1, aes(x=Var1, y=Var2, fill=value))
heatmap1 = heatmap1 + 
  geom_tile(color = "white") + 
  scale_fill_gradient(low = "blue", high = "red")

heatmap1
```

**Analysing how well participants responses in Italy predict c19ProSo02**

c19ProSo02 collects the information on how willing people are to make donations
to help others who suffer from Coronavirus. According to the summary of the 
fitted model using linear regression, PFS01 and c19NormShould appears to be the 
best predictors for this pro social behaviour due to having the lowest p-values 
among the rest of the potential predictors. jbInsec02, jbInsec03 and fail02 seem 
like potential predictors too (because a p-value lower than 0.05), but we would 
barely have enough evidence to prove of them being strong predictors. According 
to the correlation heatmap, PFS01 has a negative correlation to c19ProSo02, and
c19NormShould has a positive correlation to c19ProSo02.

```{r focuscountry_pro2}
#create datasets with only the predictors and one pro-social attribute each for linear modelling
focuscountry_pro2 = select(focuscountry_data, -c(c19ProSo01, c19ProSo03, c19ProSo04))
#create a linear regression model for all pro-social attr
italy2.fit <-lm(c19ProSo02 ~ ., data = focuscountry_pro2, na.action = na.exclude)
#check for significant predictors for all pro-social attitude attributes
summary(italy2.fit)
#plotting a correlation heatmap for c19ProSo02
focus.cor2 = as.table(round(cor(focuscountry_pro2[1:40], 
                                    use = "pairwise.complete.obs"), digit = 2))
focus.cor2 = melt(focus.cor2)
heatmap2 = ggplot(data = focus.cor2, aes(x=Var1, y=Var2, fill=value))
heatmap2 = heatmap2 + 
  geom_tile(color = "white") + 
  scale_fill_gradient(low = "blue", high = "red")

heatmap2
```

**Analysing how well participants responses in Italy predict c19ProSo03**

c19ProSo03 collects the information on how willing people are to protect vulnerable 
groups from coronavirus even at their own expense. According to the summary of the 
fitted model using linear regression, c19NormDo appears to be the best predictor 
for this pro social behaviour due to having the lowest p-values among the rest of 
the potential predictors, and a strong predictor as well. affContent is the second
best predictor after c19NormDo, and PLRAC19, fail02, fail03, edu can be considered
as potential predictors too, but we would barely have enough evidence to prove of 
them being strong predictors. According to the correlation heatmap, c19NormDo
has a positive correlation to c19ProSo03.

```{r focuscountry_pro3}
#create datasets with only the predictors and one pro-social attribute each for linear modelling
focuscountry_pro3 = select(focuscountry_data, -c(c19ProSo01, c19ProSo02, c19ProSo04))
#create a linear regression model for all pro-social attr
italy3.fit <-lm(c19ProSo03 ~ ., data = focuscountry_pro3, na.action = na.exclude)
#check for significant predictors for all pro-social attitude attributes
summary(italy3.fit)
#plotting a correlation heatmap for c19ProSo03
focus.cor3 = as.table(round(cor(focuscountry_pro3[1:40], 
                                    use = "pairwise.complete.obs"), digit = 2))
focus.cor3 = melt(focus.cor3)
heatmap3 = ggplot(data = focus.cor3, aes(x=Var1, y=Var2, fill=value))
heatmap3 = heatmap3 + 
  geom_tile(color = "white") + 
  scale_fill_gradient(low = "blue", high = "red")

heatmap3
```

**Analysing how well participants responses in Italy predict c19ProSo04**

c19ProSo04 collects the information on how willing people are to make personal 
sacrifices to prevent the spread of coronavirus. According to the summary of the 
fitted model using linear regression, fail02 and c19NormShould appears to be the 
most significant predictors for this pro social behaviour due to having the lowest 
p-values among the rest of the potential predictors. trustGovCtry and disc02 is 
the second best potential predictor, and affExc, jbInsec02, c19IsStrict, MLQ can 
be considered as potential predictors too, but we would barely have enough evidence 
to prove of them being strong predictors. According to the correlation heatmap, 
fail02 has a negative correlation to c19ProSo04, and positive correlation to
c19ProSo04.

```{r focuscountry_pro4}
#create datasets with only the predictors and one pro-social attribute each for linear modelling
focuscountry_pro4 = select(focuscountry_data, -c(c19ProSo01, c19ProSo02, c19ProSo03))
#create a linear regression model for all pro-social attr
italy4.fit <-lm(c19ProSo04 ~ ., data = focuscountry_pro4, na.action = na.exclude)
#check for significant predictors for all pro-social attitude attributes
summary(italy4.fit)
#plotting a correlation heatmap for c19ProSo04
focus.cor4 = as.table(round(cor(focuscountry_pro4[1:40], 
                                    use = "pairwise.complete.obs"), digit = 2))
focus.cor4 = melt(focus.cor4)
heatmap4 = ggplot(data = focus.cor4, aes(x=Var1, y=Var2, fill=value))
heatmap4 = heatmap4 + 
  geom_tile(color = "white") + 
  scale_fill_gradient(low = "blue", high = "red")

heatmap4
```

###### **2(c)**

**Analysing how well participants responses in other countries predict c19ProSo01**

Predictors such as affEnerg, affExh, affInsp, PLRAC19, disc02, PFS02, fail03, 
lifeSat, MLQ, c19NormShould, c19NormDo, c19IsOrg, trustGovState appear to be
significant predictors for the aforementioned pro-social behaviour. affDepr,
PLRAEco, jbInsec04, fail01, fail02, c19IsStrict, gender are the next best
predictors with a relatively low p-value as well. 

```{r othercountries_pro1}
#create data sets with only the predictors and one pro-social attribute each for linear modelling
othercountries_pro1 = select(othercountries_data, -c(c19ProSo02, c19ProSo03, c19ProSo04))
#create a linear regression model for all pro-social attr
other1.fit <-lm(c19ProSo01 ~ ., data = othercountries_pro1, na.action = na.exclude)
#check for significant predictors for all pro-social attitude attributes
summary(other1.fit)
#plotting a correlation heatmap for c19ProSo01
other.cor1 = as.table(round(cor(othercountries_pro1[1:40], 
                                    use = "pairwise.complete.obs"), digit = 2))
other.cor1 = melt(other.cor1)
heatmap5 = ggplot(data = other.cor1, aes(x=Var1, y=Var2, fill=value))
heatmap5 = heatmap5 + 
  geom_tile(color = "white") + 
  scale_fill_gradient(low = "blue", high = "red")

heatmap5
```

**Analysing how well participants responses in other countries predict c19ProSo02**

Predictors such as affAnx, affBor, affExc, affExh, affInsp, PLRAEco, disc02,
disc03, jbInsec02, PFS01, fail01, lifeSat, MLQ, c19NormShould, c19NormDo, 
c19IsOrg, trustGovState, age and edu are all strong predictors. jbInsec01, 
trustGovCtry are the next best predictors. 

```{r othercountries_pro2}
#create datasets with only the predictors and one pro-social attribute each for linear modelling
othercountries_pro2 = select(othercountries_data, -c(c19ProSo01, c19ProSo03, c19ProSo04))
#create a linear regression model for all pro-social attr
other2.fit <-lm(c19ProSo02 ~ ., data = othercountries_pro2, na.action = na.exclude)
#check for significant predictors for all pro-social attitude attributes
summary(other2.fit)
#plotting a correlation heatmap for c19ProSo02
other.cor2 = as.table(round(cor(othercountries_pro2[1:40], 
                                    use = "pairwise.complete.obs"), digit = 2))
other.cor2 = melt(other.cor2)
heatmap6 = ggplot(data = other.cor2, aes(x=Var1, y=Var2, fill=value))
heatmap6 = heatmap6 + 
  geom_tile(color = "white") + 
  scale_fill_gradient(low = "blue", high = "red")

heatmap6
```

**Analysing how well participants responses in other countries predict c19ProSo03**

affDepr, affExh, affInsp, PLRAC19, disc02, disc03, PFS01, fail01, fail03, lifeSat,
MLQ, c19NormShould, c19NormDo, c19IsOrg, trustGovCtry, trustGovState, age, edu
all appear to be significant predictors of c19ProSo03. 

```{r othercountries_pro3}
#create datasets with only the predictors and one pro-social attribute each for linear modelling
othercountries_pro3 = select(othercountries_data, -c(c19ProSo01, c19ProSo02, c19ProSo04))
#create a linear regression model for all pro-social attr
other3.fit <-lm(c19ProSo03 ~ ., data = othercountries_pro3, na.action = na.exclude)
#check for significant predictors for all pro-social attitude attributes
summary(other3.fit)
#plotting a correlation heatmap for c19ProSo03
other.cor3 = as.table(round(cor(othercountries_pro3[1:40], 
                                    use = "pairwise.complete.obs"), digit = 2))
other.cor3 = melt(other.cor3)
heatmap7 = ggplot(data = other.cor3, aes(x=Var1, y=Var2, fill=value))
heatmap7 = heatmap7 + 
  geom_tile(color = "white") + 
  scale_fill_gradient(low = "blue", high = "red")

heatmap7
```

**Analysing how well participants responses in other countries predict c19ProSo04**

affExh, PLRAC19, disc02, jbInsec02, PFS02, fail01, fail02, fail03, lifeSat,
c19NormShould, c19IsStrict, c19IsPunish, c19IsOrg, trustGovState and age are the
most significant predictors for c19ProSo04. jbInsec01, MLQ and trustGovCtry come
in next as best predictors.

```{r othercountries_pro4}
#create datasets with only the predictors and one pro-social attribute each for linear modelling
othercountries_pro4 = select(othercountries_data, -c(c19ProSo01, c19ProSo02, c19ProSo03))
#create a linear regression model for all pro-social attr
other4.fit <-lm(c19ProSo04 ~ ., data = othercountries_pro4, na.action = na.exclude)
#check for significant predictors for all pro-social attitude attributes
summary(other4.fit)
#plotting a correlation heatmap for c19ProSo02
other.cor4 = as.table(round(cor(othercountries_pro4[1:40], 
                                    use = "pairwise.complete.obs"), digit = 2))
other.cor4 = melt(other.cor4)
heatmap8 = ggplot(data = other.cor4, aes(x=Var1, y=Var2, fill=value))
heatmap8 = heatmap8 + 
  geom_tile(color = "white") + 
  scale_fill_gradient(low = "blue", high = "red")

heatmap8
```

**Comparing attributes that are deemed as strong predictors of pro social behaviours between other countries and focus country**

**T-test for c19NormShould**

c19NormShould is a strong predictor for both Italy and other countries in response
to pro social behaviours. Test whether people in other countries believe that
people should self isolate and engage in social distancing more than the people
of Italy. 
```{r hypothesis_test_c19NormShould}
# Apply 2 sample hypothesis test
t.test(othercountries_data$c19NormShould, focuscountry_data$c19NormShould, "greater",
conf.level = 0.95)
```
From the result above, the null hypothesis is accepted, which means people of
Italy and other countries both have the same opinion on which degree people
should self isolate and engage in social distancing because the p-value is larger
than 0.05.

**T-test for jbInsec02**

jbInsec02 appeared to be significant predictors for c19ProSo01 in Italy and 
c19ProSo04 in other countries. Test whether the people in Italy are more certain
that they can keep their job as compared to people in other countries.
```{r hypothesis_test_jbInsec02}
# Apply 2 sample hypothesis test
t.test(othercountries_data$jbInsec02, focuscountry_data$jbInsec02, "less",
conf.level = 0.95)
```
We can conclude that the null hypothesis is accepted, citizens of Italy and other
countries have the same certainty on whether or not they are able to keep their
jobs, as the p-value is more than 0.05.

**T-test for c19NormDo**

c19NormDo is another significant predictor for many pro-social behaviors. Test
whether people in Italy believe that their community does self isolation and 
engage in social distancing more than what people in other countries think.
```{r hypothesis_test_c19NormDo}
# Apply 2 sample hypothesis test
t.test(othercountries_data$c19NormDo, focuscountry_data$c19NormDo, "less",
conf.level = 0.95)
```
It is concluded that the null hypothesis is accepted, which means the people
from both locations have the same opinion on whether societies in their respective
countries do self isolation and engage in social distancing. This is due to the
p-value being larger than 0.05.

**T-test for PFS01**

Test whether the people in other countries feel more financially strained
compared to Italians.
```{r hypothesis_test_PFS01}
# Apply 2 sample hypothesis test
t.test(othercountries_data$PFS01, focuscountry_data$PFS01, "greater",
conf.level = 0.95)
```
Based on the results above, we can safely reject the null hypothesis as the 
p-value is lesser than 0.05. This means that there is enough evidence to prove 
that people in other countries indeed experience more financial strain as 
compared to Italy.

**T-test for fail02**

fail02 asks to agree or disagree that, if one compares themselves to others in 
their own country, their group is worse off. Test whether Italians agree to the 
statement of fail02 more than people in other countries.
```{r hypothesis_test_fail02}
# Apply 2 sample hypothesis test
t.test(focuscountry_data$fail02, othercountries_data$fail02, "greater",
conf.level = 0.95)
```
We are able to deduce that the null hypothesis is rejected, where the p-value
is lesser than 0.05, therefore there is enough evidence to prove that Italians,
on the scale from strongly disagree to strongly agree, are leaning more towards
the right of the scale compared to people in other countries.

##### **Question 3**

###### **3(a)**

Indicators used: coded_country, disc01, disc02, disc03, jbInsec02, PFS01, 
PFS02, PFS03, fail01, fail02, fail03, lifeSat, MLQ, c19NormShould, c19NormDo, 
trustGovCtry, trustGovState, c19ProSo01, c19ProSo02, c19ProSo03, c19ProSo04

```{r k-means clustering}
#choose indicators to be part of the data used for clustering
cluster_data = select(clean_cvbase, c(coded_country,disc01, disc02, disc03, jbInsec02, PFS01, 
                                      PFS02, PFS03, fail01, fail02, fail03, lifeSat, MLQ, c19NormShould, 
                                      c19NormDo, trustGovCtry, trustGovState, c19ProSo01, c19ProSo02,
                                      c19ProSo03, c19ProSo04))

#scale the data
cluster_data = na.omit(cluster_data)
scaled_cluster_data = scale(cluster_data[,2:21])

# Applying the average silhouette score to find the optimal number of clusters

# make function to get average silhouette score
i_silhouette_score <- function(k){
  km <- kmeans(scaled_cluster_data, centers = k, nstart=25)
  ss <- silhouette(km$cluster, dist(scaled_cluster_data))
  mean(ss[, 3], na.rm = TRUE)
}

#plot average silhouette score for 2-10 clusters
k = 2:10
avg_sil <- sapply(k, i_silhouette_score)
plot(k, type='b', avg_sil, xlab='Number of clusters', ylab='Average Silhouette
Scores')

# 4 was chosen as the optimal number of clusters
# performing k-means clustering
CDkfit = kmeans(scaled_cluster_data, 4, nstart = 20)
T1 = table(actual = cluster_data$coded_country, fitted = CDkfit$cluster)
T1 = as.data.frame.matrix(T1)

#clustering visualisation
fviz_cluster(CDkfit, data = scaled_cluster_data,
             palette = c("#2E9FDF", "#00AFBB", "#E7B800", "#AA336A"),
             geom = "point",
             ellipse.type = "convex",
             ggtheme = theme_bw()
             )
```

After performing clustering, Australia, Canada and Brazil can be deemed to be 
similar to Italy in their responses towards the indicators used for clustering.
This is because all 4 countries had the majority of observations clustered into
group 3, with the total respondant size being a similar sizes as well (between
400 to 700).

###### **3(b)**

```{r cluster_grouping}
temp1 <- clean_cvbase[(clean_cvbase$coded_country == "Australia"),]
temp2 <- clean_cvbase[(clean_cvbase$coded_country == "Brazil"),]
temp3 <- clean_cvbase[(clean_cvbase$coded_country == "Canada"),]
clustercountry_data <- rbind(temp1, temp2, temp3)
rownames(clustercountry_data) <- 1:nrow(clustercountry_data)
```

**Analysing how well participants responses in cluster countries predict c19ProSo01**

According to the summary of the fitted model using linear regression, jbInsec02 
and c19NormShould appears to be the best predictors for this pro social behaviour 
due to having the lowest p-values among the rest of the potential predictors.

```{r clustercountry_pro1}
#create data sets with only the predictors and one pro-social attribute each for linear modelling
clustercountries_pro1 = select(clustercountry_data, -c(c19ProSo02, c19ProSo03, c19ProSo04))
#create a linear regression model for all pro-social attr
cluster1.fit <-lm(c19ProSo01 ~ ., data = focuscountry_pro1, na.action = na.exclude)
#check for significant predictors for all pro-social attitude attributes
summary(cluster1.fit)
```

**Analysing how well participants responses in cluster countries predict c19ProSo02**

According to the summary of the fitted model using linear regression, c19NormShould 
and PFS01 appears to be the best predictors for this pro social behaviour due to 
having the lowest p-values among the rest of the potential predictors.

```{r clustercountry_pro2}
#create data sets with only the predictors and one pro-social attribute each for linear modelling
clustercountries_pro2 = select(clustercountry_data, -c(c19ProSo01, c19ProSo03, c19ProSo04))
#create a linear regression model for all pro-social attr
cluster2.fit <-lm(c19ProSo02 ~ ., data = focuscountry_pro2, na.action = na.exclude)
#check for significant predictors for all pro-social attitude attributes
summary(cluster2.fit)
```

**Analysing how well participants responses in cluster countries predict c19ProSo03**

According to the summary of the fitted model using linear regression, c19NormDo 
appears to be the best predictors for this pro social behaviour due to having the 
lowest p-values among the rest of the potential predictors. The next best predictor
is affContent.

```{r clustercountry_pro3}
#create data sets with only the predictors and one pro-social attribute each for linear modelling
clustercountries_pro3 = select(clustercountry_data, -c(c19ProSo01, c19ProSo02, c19ProSo04))
#create a linear regression model for all pro-social attr
cluster3.fit <-lm(c19ProSo03 ~ ., data = focuscountry_pro3, na.action = na.exclude)
#check for significant predictors for all pro-social attitude attributes
summary(cluster3.fit)
```

**Analysing how well participants responses in cluster countries predict c19ProSo04**

According to the summary of the fitted model using linear regression, fail02 
and c19NormShould appears to be the most significant predictors for this pro 
social behaviour. 

```{r clustercountry_pro4}
#create data sets with only the predictors and one pro-social attribute each for linear modelling
clustercountries_pro4 = select(clustercountry_data, -c(c19ProSo01, c19ProSo02, c19ProSo03))
#create a linear regression model for all pro-social attr
cluster4.fit <-lm(c19ProSo04 ~ ., data = focuscountry_pro4, na.action = na.exclude)
#check for significant predictors for all pro-social attitude attributes
summary(cluster4.fit)
```

**T-test for jbInsec02**

jbInsec02 appeared to be significant predictors for c19ProSo01 in Italy and 
cluster countries as well. Test whether the people in Italy are more certain
that they can keep their job as compared to people in cluster countries.
```{r hypothesis_test_jbInsec02_cluster}
# Apply 2 sample hypothesis test
t.test(clustercountry_data$jbInsec02, focuscountry_data$jbInsec02, "less",
conf.level = 0.95)
```
We can conclude that the null hypothesis is accepted, citizens of Italy and cluster
countries have the same certainty on whether or not they are able to keep their
jobs, as the p-value is more than 0.05.

**T-test for c19NormShould**

Test whether people in cluster countries believe that people should self isolate 
and engage in social distancing more than the people of Italy. 
```{r hypothesis_test_c19NormShould_cluster}
# Apply 2 sample hypothesis test
t.test(clustercountry_data$c19NormShould, focuscountry_data$c19NormShould, "greater",
conf.level = 0.95)
```
From the result above, there is enough evidence to reject the null hypothesis as
the p-value is smaller than 0.05. This means people of the cluster countries do
believe more that people should self isolate and engage in social distancing than
Italians.

**T-test for PFS01**

Test whether the people in cluster countries feel more financially strained
compared to Italians.
```{r hypothesis_test_PFS01_cluster}
# Apply 2 sample hypothesis test
t.test(clustercountry_data$PFS01, focuscountry_data$PFS01, "greater",
conf.level = 0.95)
```
Based on the results above, we can safely reject the null hypothesis as the 
p-value is lesser than 0.05. This means that there is enough evidence to prove 
that people in cluster countries indeed experience more financial strain as 
compared to Italy.

**T-test for c19NormDo**

Test whether people in Italy believe that their community does self isolation and 
engage in social distancing more than what people in cluster countries think.
```{r hypothesis_test_c19NormDo_cluster}
# Apply 2 sample hypothesis test
t.test(clustercountry_data$c19NormDo, focuscountry_data$c19NormDo, "less",
conf.level = 0.95)
```
It is concluded that the null hypothesis is accepted, which means the people
from both locations have the same opinion on whether societies in their respective
countries do self isolation and engage in social distancing. This is due to the
p-value being larger than 0.05.

**T-test for fail02**

fail02 asks to agree or disagree that, if one compares themselves to others in 
their own country, their group is worse off. Test whether Italians agree to the 
statement of fail02 more than people in cluster countries.
```{r hypothesis_test_fail02_cluster}
# Apply 2 sample hypothesis test
t.test(focuscountry_data$fail02, clustercountry_data$fail02, "greater",
conf.level = 0.95)
```
We are able to deduce that the null hypothesis is rejected, where the p-value
is lesser than 0.05, therefore there is enough evidence to prove that Italians,
on the scale from strongly disagree to strongly agree, are leaning more towards
the right of the scale compared to people in cluster countries.

**Discussion**

After analysing the best predictors for the cluster countries, it is found that
these predictors are the most significant predictors for focus country (Italy)
in regards to every pro social behaviour as well. The comparison of predictors
between Italy vs other countries and Italy vs cluster countries have resulted
to the same outcome, except for c19NormShould where there was indeed a difference
in responses between the focus country and the cluster countries. In summary, the
attributes predicted as significant predictors are definitely a better match to
project pro social behaviours in the focus country Italy as they are a total
match. 

#### **Appendix**

*Assumption #1*

Every record is deemed to have NA values as the attributes that involve employment 
status is not meant to be filled up entirely, for example some people may be 
students,hence they are unemployed, whereas working individuals will choose the 
choices with employment involved.

*R packages used*

- ggplot2
- dplyr
- tidyr
- factoextra

*R libraries loaded*

- ggplot2
- tidyr
- dplyr
- reshape2 
- cluster
- factoextra




